---
title: "Utility Costs in Ireland"
author: "J.Phillips"
date: "16 September 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
This project visualises the cost of electricity and gas for a 3 bedroom house in Dublin, Ireland between 2013 and 2016. The house uses a gas boiler for heating.

---

### Dataset

This dataset was created from old paper bills that I had hanging around before we changed providers and the bills moved online. If I could find the password to that account, I would add the subsequent years in - but it is proving to be elusive at the moment.

```{r echo=FALSE}
df <- read.csv("./data/gas-electricity-prices.csv")
head(df)
```

---

### Data manipulation

As the date range of each bill varied quite widely, I divided the total cost by the number of days in the date range to obtain the cost in Euros per day.

```{r eval=FALSE}
for (i in 1:dim(df)[1]) {
    startDt <- df$start_date[i]
    endDt <- df$end_date[i]
    dates <- seq.Date(startDt, endDt, "day")
    df$total_days[i] <- length(dates)
    # calculate per day rate
    df$amount_per_day[i] <- as.numeric(
        as.character(format(
            round(
                df$amount[i] / df$total_days[i], 
                digits=2), nsmall=2)))
}
```

---

### Instructions

- Use the slider in the side panel to select the date range.

- Use the dropdown list to select what you want to plot.

- Use the checkbox to see a more detailed description.

Note that the y-axis range changes depending on which plot you choose. Selecting to view only electricity gives a clearer view of the seasonal cost fluctuation although it is much less evident than the seasonal cost fluctuation of gas.

